Short and Mechanized Logical Relation for Dependent Type Theory

### 2024-02-23 paper/paper.tex
Update line count and minor rewording

\scw{Name and foreshadow these lemmas when they are introduced so that
it is easier to refer to them in the discussion.}
Finally, we want to point out that
the adequacy property (Lemma~\ref{lemma:adequacy}) are in fact required in the normalization proof
for simply typed languages~\citep{abel2019poplmark}. Similar to the
simply typed scenario, adequacy needs to be proven before the
fundamental theorem so we can handle elimination rules such as
\rref{T-If} and \rref{T-App} where the scrutinee is a neutral term. In
\citet{abel2019poplmark}, a variant of Lemma~\ref{lemma:extwn} is used
in the exact same way to show the normalization of lambda forms
as we have done in Lemma~\ref{lemma:crel}.

Dependent types make the adequacy proof slightly more complicated
as we also need to know that every type has a normal form, not just
the terms.
This complicates our proof specifically in the \rref{I-Set} case for
Lemma~\ref{lemma:adequacy}.

@@

\section{Mechanization}
\label{sec:logrelmech}
\begin{figure}[h]
  \begin{tabular}{ c |  c  | c  }
    & Consistency & Normalization \\
    \hline
    % Library (Autosubst 2)  & 491 & - \\
    Syntactic typing (specification) &  69 & - \\
    Renaming & 46 & -  \\
    % Syntactic soundness & 660 &  - \\
    Untyped reduction & 350 & 834 \\
    Logical relation & 342 & 515 \\
    Semantic typing and soundness & 169 & 197 \\
  \end{tabular}
  \caption{Statistics of the Coq Development}
  \label{fig:linecount}
\end{figure}

>>>>

\scw{Name and foreshadow these lemmas when they are introduced so that
it is easier to refer to them in the discussion.}
Finally, we want to point out that
the adequacy property (Lemma~\ref{lemma:adequacy}) are in fact required in the normalization proof
for simply typed languages~\citep{abel2019poplmark}. Similar to the
simply typed scenario, adequacy needs to be proven before the
fundamental theorem so we can handle elimination rules such as
\rref{T-If} and \rref{T-App} where the scrutinee is a neutral term. % In
% \citet{abel2019poplmark}, a variant of Lemma~\ref{lemma:extwn} is used
% in the exact same way to show the normalization of lambda forms
Dependent types make the adequacy proof slightly more complicated
as we also need to know that every type has a normal form, not just
the terms.
This complicates our proof specifically in the \rref{I-Set} case for
our adequacy property (Lemma~\ref{lemma:adequacy}).

@@

\section{Mechanization}
\label{sec:logrelmech}
\begin{figure}[h]
  \begin{tabular}{ c |  c  | c  }
    & Consistency & Normalization \\
    \hline
    % Library (Autosubst 2)  & 491 & - \\
    Syntactic typing (specification) &  68 & - \\
    Renaming & 46 & -  \\
    % Syntactic soundness & 660 &  - \\
    Untyped reduction & 349 & - \\
    Neutral and normal forms & N/A & 269 \\
    Logical relation & 331 & 426 \\
    Semantic typing and soundness & 169 & 199 \\
    \hline
    Total & 963 & 1357 \\
  \end{tabular}
  \caption{Statistics of the Coq Development}
  \label{fig:linecount}
\end{figure}
